\newcommand{\low}{\cellcolor{green}Low}
\newcommand{\medium}{\cellcolor{orange}Medium}
\newcommand{\high}{\cellcolor{red}High}
\begin{longtable}{|l|p{5cm}|l|l|l|p{4cm}|p{5cm}|}
	\hline
	\textbf{Category} & \textbf{Name} & \textbf{Severity} & \textbf{Likelihood} & \textbf{Overall} & \textbf{Mitigation} & \textbf{Contingency} \\ \hline \hline
	\endhead
	Staff & Team member leaves & High & Low & \medium & & \\ \hline
	Staff & Staff sick or unable to attend meetings. & Medium & High & \high & Let other members of the team know as soon as possible & Other staff takes over their work temporarily. \\ \hline
	Staff & Don’t have the skill required to complete the task. & Low & Medium & \low & Research the skills needed. Ask other team members if they know how to help. & Read books and the internet about required skills. \\ \hline
	Staff & Staff don’t listen others opinion& Low & Low & \low & More communication, consult Richard/Fiona if the problem continues. & Stay together and work out the root reason, then resolve it. \\ \hline
	
	Staff/Requirements & Staff failed to complete the task before deadline. & High & Low & \medium & More rapid sprint to ensure everyone is on track. & Cut our optional features and complete the compulsory requirements first. \\ \hline
	
	Requirements & Change of requirements & Low & High & \medium & Keep in touch, build and show to the client & Update the requirement document and update the product. \\ \hline
	Requirements & Responsible of telling the customer that requirements were impossible and offer alternative options. & Low & Low & \low & Negotiate with the customer before updating the requirements. & Explain to the customer what has to be changed. \\ \hline
	Requirements & Cannot meet the requirement & High & Low & \medium & Design realistic requirements before start coding. & Modify the requirements so it can be met. \\ \hline
	
	Tech & Data lost - e.g. hard drive failure. & Medium & Low & \low & Backup data regularly to cloud or different devices. & Restore most recent backed up data. \\ \hline
	Tech & IT facility failure & Low & Low & \low & Routine maintenance to devices. & Use campus computer to continue development. \\ \hline
	Tech & Security threats & High & Low & \medium &  Install antivirus software and enable firewall. & Seek IT support for help and continue working. \\ \hline
	Tech & Software bug that causes data loss. & High & Medium & \high & Backup data before executing dangerous commands. & Reset to the previous commit using git. \\ \hline
	
	Tools & Tools not available & Low & Medium & \low & Research background information about alternatives before proceeding. & Switch to an alternative tool, request help from IT support or create one if enough time before deadline. \\ \hline
	Tools & Unfamiliar with the toolset. & Low & Medium & \low & Learn how to use the tool. & Ask IT support or other teammates for help. \\ \hline
	Tools & Tools does not fit into the project after start off. & Low & Medium & \low & Do extensive research and comparison before integrating to the workflow. & Find alternative and re-evaluate options. \\ \hline
	
	Estimation & Estimates that there will not be enough time to finish the whole project. & High & Medium & \high & Allocate and plan the time efficiently. & Plan and spend more time for the project. \\ \hline
	
	Customer & Customer changes the requirements. & Low & High & \medium & Keep in touch and understand the necessary changes as soon as possible. & Examine new requirements and update them accordingly. \\ \hline
	Customer & Customer doesn't allow or understand why we have to change the requirements. & Medium & Medium & \medium & Keep in touch with the customer & Sit next with the customer and talk through the reason why. \\ \hline
	
	Test & Bugs discovered & Medium & High & \high & Understand the code and have comments around them. & Fix bugs. \\ \hline
	Test & Something wrong but cannot find the errors. & Medium & Medium & \medium & Put comment around the code to describe, and do tests. & Debug the problem using a debugger and seek for help. \\ \hline
	
\end{longtable}